Interval Probability and Measurement for Fuzzy Quantum Theories

### 2016-10-19 prob.tex
prob.tex "\subsection{Classical Real-Valued Probability Spaces}" Matching parathesis...

\begin{definition}[Probability Measure]\label{def:ClassicalProbabilitySpace}
Given the set of events $\events$, a \emph{probability measure} is
a function $\pmeas:\events\rightarrow[0,1]$ such that: 
\begin{itemize}
\item $\pmeas(\emptyset)=0$. 
\item $\pmeas(\Omega)=1$. 
\item For any event $E$, 
\begin{equation}
\pmeas\left(\Omega\backslash E\right)=1\tensor*[_{\mathbb{R}}]{-}{}\pmeas\left(E\right)\textrm{ ,}\label{eq:ClassicalReal-valuedProbability-Complement}
\end{equation}
where $\Omega\backslash E$ is the complement event, and $1\tensor*[_{\mathbb{R}}]{-}{}\pmeas\left(E\right)$
explicitly specifies $1$ and $\pmeas\left(E\right)\in\mathbb{R}$.
Besides $\mathbb{R}$, we will prepose other symbols later to specify
the type of operations, and they may be dropped when there is no ambiguity. 
\item For a collection $\left\{ E_{i}\right\} _{i=0}^{N-1}$ of pairwise
disjoint events, $\pmeas(\bigcup_{i=0}^{N-1}E_{i})=\tensor*[_{\mathbb{R}}]{\sum}{_{i=0}^{N-1}}\pmeas(E_{i})$.
Similar to the above condition, $\tensor*[_{\mathbb{R}}]{\sum}{_{i=0}^{N-1}}\pmeas(E_{i})$
explicitly specifies $\pmeas(E_{i})\in\mathbb{R}$. 
\end{itemize}
\qed\end{definition}

>>>>

\begin{definition}[Probability Measure]\label{def:ClassicalProbabilitySpace}
Given the set of events $\events$, a \emph{probability measure} is
a function $\pmeas:\events\rightarrow[0,1]$ such that: 
\begin{itemize}
\item $\pmeas(\emptyset)=0$. 
\item $\pmeas(\Omega)=1$. 
\item For any event $E$, 
\begin{equation}
\pmeas\left(\Omega\backslash E\right)=1\tensor*[_{\mathbb{R}}]{-}{}\pmeas\left(E\right)\textrm{ ,}\label{eq:ClassicalReal-valuedProbability-Complement}
\end{equation}
where $\Omega\backslash E$ is the complement event, and $1\tensor*[_{\mathbb{R}}]{-}{}\pmeas\left(E\right)$
explicitly specifies $1$ and $\pmeas\left(E\right)\in\mathbb{R}$.
Besides $\mathbb{R}$, we will prepose other symbols later to specify
the type of operations, and they may be dropped when there is no ambiguity. 
\item For a collection $\left\{ E_{i}\right\} _{i=0}^{N-1}$ of pairwise
disjoint events, $\pmeas\left(\bigcup_{i=0}^{N-1}E_{i}\right)=\tensor*[_{\mathbb{R}}]{\sum}{_{i=0}^{N-1}}\pmeas(E_{i})$.
Similar to the above condition, $\tensor*[_{\mathbb{R}}]{\sum}{_{i=0}^{N-1}}\pmeas(E_{i})$
explicitly specifies $\pmeas(E_{i})\in\mathbb{R}$. 
\end{itemize}
\qed\end{definition}
